% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,12pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.2in}
\addtolength{\textheight}{1.0in}
\usepackage[pdftex,
            pdfauthor={Arnau Casas Saez},
            pdftitle={Arnau's resume},
            pdfsubject={Arnau Casas Saez personal resume and CV},
            pdfkeywords={resume, cv, Arnau Casas, software engineer,},
            pdfproducer={Latex with hyperref},
            pdfcreator={pdflatex, or other tool}]{hyperref}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadinged}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4}\\
\end{tabular*}\vspace{-6pt}}

\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1}%
}

%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
 \textbf{\large Arnau Casas Saez}& \href{mailto:casassarnau@gmail.com}{casassarnau@gmail.com} \\
 & +34 651 84 29 80
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
	\begin{itemize}

		\item
			\ressubheadinged{Universitat Polit\`ecnica de Catalunya}{Barcelona, Spain}{B.S., Computer Science (8.63/10)}{September 2018 - Present}
			\begin{itemize}
				\resitem{\textbf{Courses:} Introduction to Computers, Physics, Programming I \& II, Fundamentals of Mathematics, Mathematics I \& II, Computer Organization, Data Structures and Algorithmics, Computer Interfacing, Probability and Statistics, Databases, Operating Systems, Interaction and Interface Design, Computer Architecture, Business and Economic Environment, Introduction to Software Engineering, Computer Networks.}
			\end{itemize}

        \item
			\ressubheadinged{Santa Teresa de Lisieux}{Barcelona, Spain}{High School, Technology (8.56/10)}{September 2016 - June 2018}
			
			
	\end{itemize}

% \resheading{Research experience}
% 	\begin{itemize}
% 		\item
% 			\ressubheading{Project EPIC, Colorado University}{Boulder, CO}{Research intern}{Research intern, February 2017 - present}
% 			\begin{itemize}
% 				\item Developed infrastructure to collect and analyze Twitter data in real time with an average of 2000 tweets/minute
% 				\item Written \textit{Big Data Analytics in Container Orchestrated Systems} as my B.S. thesis.
% 				\item Designed and built big data analytics system prototype on Kubernetes.
% 			\end{itemize}
% 	\end{itemize}

\resheading{Experience}
	\begin{itemize}
		\item
			\ressubheading{HackUPC}{Barcelona, Spain}{Web developer}{Web developer director, March 2019 - Present}
			\begin{itemize}
				\resitem{Developed mentorship platform frontend for Spain's largest hackathon using React.js.}
				\resitem{Developed a check in and baggage App for organizers of HackUPC using Kotlin.}
				\resitem{Developed new API and features for mentors and volunteers for the main platform of HackUPC using Django.}
			\end{itemize}
		\item
			\ressubheading{YMCA of Greater Indianapolis}{St. Paul, IN}{Junior Summer Camp Counselor}{Junior Summer Camp Counselor, Summer 2018}
			\begin{itemize}
				\resitem{Supervised groups of 12 campers in resident camp setting.}
				\resitem{Responsible for creating and managing activities autonomously such as archery, kayaking, etc.}
			\end{itemize}

	\end{itemize}

\resheading{Projects}
	\begin{itemize}
		\item
			\ressubheading{Kalorika}{Barcelona, Spain}{Student}{Spring 2017}
			\begin{itemize}
				\resitem{Developed prototype web app in Flask and Python to reduce children's obesity by analyzing nutritional information from images.}
				\resitem{Integrated with Clarifai API and Edamam API for image processing and image information.}
			\end{itemize}
		\item
			\ressubheading{Solvat Renovables web page}{Barcelona, Spain}{Student}{Summer 2020}
			\begin{itemize}
				\resitem{Developed webpage for Solvat Renovables Enterprise with Django framework and PostgressSQL}
			\end{itemize}
	\end{itemize}

% \resheading{Leadership}
% 	\begin{itemize}
% 		\item 
% 			\ressubheading{HackCU, University of Colorado Boulder}{Boulder, CO}{Tech director}{Tech director, February 2017 - April 2019}
% 			\begin{itemize}
% 				\resitem{Co-directed Colorado's biggest student hackathon with 600 attendees and a 15 people core team.}
% 			\end{itemize}
% 		\item
% 			\ressubheading{HackUPC, Universitat Polit\`ecnica de Catalunya}{Barcelona, Spain}{Co-Director and organizer}{Co-Director, November 2015 - September 2018}
% 			\begin{itemize}
% 				\resitem{Co-directed Spain's biggest student hackathon with 500 attendees and a 20 people core team.}
% 				% \item Directed web development team with 5 person team for 2 editions.
% 			\end{itemize}
% 	\end{itemize}

\resheading{Awards}
	\begin{itemize}
		\resitem{\textbf{Best project in "19\`e F\`orum de recerca de les corts" from 20 selected best projects of Les Corts. With "Kalorika".} (2018)}
		\resitem{\textbf{Best project in "Mostra de Recerca jove" from 200 selected best projects of Barcelona. With "Kalorika".} (2018)}
	\end{itemize}

% \resheading{Publications}
% 	\begin{itemize}
% 		\item 	Jennings A., Gerard C., Kenneth M. A., Leysia P., and Rebecca M.  \textbf{Incorporating Context and Location Into Social Media Analysis: A Scalable, Cloud-Based Approach for More Powerful Data Science.}  \textit{HICSS 52 (accepted).}
%         \item Gerard C. \textbf{Social Media Analysis for Crisis Informatics in the Cloud} \textit{MS Thesis}
% 	\end{itemize}


\resheading{Skills}
	\begin{itemize}
		\resitem{\textbf{Programming experience:} Python, C++, Javascript, Flask, HTML, CSS, Git, Kotlin, Django.}
		\resitem{\textbf{Native languages:} Catalan, Spanish.}
		\resitem{ \textbf{Advanced:} English - Spent 4 summers in a US camp.}
		\resitem{\textbf{Hobbies:} Roller Hockey, swimming, kayaking, archery.}
		\resitem{\textbf{Hackathon participation:} HackUPC (organizer), Hacktoberfest, HackEPS.}
	\end{itemize}



\end{document}

